---
aliases: [up-and-running-with-blogdown]
projects: [up-running-blogdown]
title: Up & Running with blogdown
authors: [alison]
date: '2017-06-12'
tags: [blogdown]
categories:
  - blogdown
  - hugo
  - netlify
summary: A guide to getting up and running with blogdown, GitHub, and Netlify
image:
  caption: '[Photo by Lindsay Henwood on Unsplash](https://unsplash.com/photos/7_kRuX1hSXM)'
  focal_point: ''
output:
  blogdown::html_page:
    toc: true
    number_sections: true
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('leaflet')
library('knitr')
library('kableExtra')
```
Because what good is a website if you can't put something interactive on it?

This is a bit of code mapping some of our study villages in Mali. It uses the leaflet package for visualization.

First, make a data frame of points:

```{r}

Pin <- data.frame(site=c("Thierola", "Siguima", "Markabougou", "Dallowere", "Niono",
                        "Konani", "Diessourouna", "Torodo", "Zanga", "M'Piabougou",
                        "N'Gabakoro", "Bia", "Guemou"),
                 latitude = c(13.6586, 14.16762, 13.91442, 13.61576, 14.223473,
                              13.9513, 13.9289, 13.0791, 13.688050, 13.599830,
                              12.683870, 10.42, 14.5476),
                 longitude = c(-7.21471, -7.22793, -6.34382, -7.03689, -6.051057,
                               -6.9708, -6.7094, -8.3589, -7.221029, -7.192859,
                               -7.840419, -5.87, -9.31067))
Pin %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

Then create the leaflet app:
``` {r leaflet}
leaflet(data = Pin) %>% addTiles() %>%
  addMarkers(~longitude, ~latitude, popup = ~as.character(site), label = ~as.character(site)) %>%
  addProviderTiles(providers$Esri.WorldImagery, group="ESRI.WorldImagery") %>%
  addProviderTiles(providers$CartoDB.PositronOnlyLabels, group="ESRI.WorldImagery") %>%   
  addLayersControl(
     baseGroups = c("OSM (default)", "ESRI.WorldImagery"),
     options = layersControlOptions(collapsed = FALSE))

```

This includes two different tiles that you can toggle (Esri.WorldImagery and CartoDB). If you want more tiles--- look [here](http://leaflet-extras.github.io/leaflet-providers/preview/).

The addLayersControl option provides the toggle itself.

These maps are rather customizable, but I have noticed that there is limited ability to deal with dense points (via either something analogous to ggrepel with ggplot or fading labels as you see in google earth). Maybe something to look into in the future.
